Contracts for unions and intersections are hard for Nickel

### 2021-06-07 paper.tex
Sections 2&3: superficial (spelling, etc…) pass

\subsection*{Code manipulation (optimizations)}
\label{sec:optimizations}
\info{Present inlining and CSE as two major code
optimizations.
Purity and immutability as two important factors.}

@@

Beyond CSE, optimizations such as loop-invariant code motion or
let-floating~\cite{letFloating} apply the same principle of extracting out an invariant
\unsure{Was this the inteded citation?}
expression to avoid its recomputation respectively across loop iterations and
function calls.

@@

\unsure{Should we tease already here that unions and intersections break this
even for pure terms?}

\subsection*{Lazyness}
\todo{Lazyness does not appear on sec 4, if we don't put somethign there, I'd remove it}
Evaluation strategies relates to the evaluation of the expression bound to
identifiers. Expressions are bound by assignments (e.g. let bindings in
Nickel), or by function applications (arguments are bound to parameters). We
will use Figure~\ref{} as a working example.

The eager strategy consists in evaluating right away a bound value before
storing it in an identifier. If an identifier is not used, this leads to
unnecessary work: in Figure~\ref{}, the expression \nickel{fibonacci 100} would
be computed although it is never used. The lazy strategy, on the other hand,
only evaluates expression if they are needed. In the lazy model, bound
expressions are stored as in their current unevaluated form, also called a
\emph{thunk}. Thunks are only evaluated at their first usage, and their value is
memoized for future usages.

The eager strategy has been chosen in the vast majority of languages: while
theoretically less efficient, it is simpler to implement and more predictable
for the programmer. Also, lazy evaluation can occur performance overhead and
memory leaks in unexpected ways. While eager evaluation is the default, some
languages however offer a form of lazy evaluation, either as an opt-in option
(e.g. Ocaml and ReScript), or by default for specific primitives types such as
list (e.g.  Swift and Perl6). The most notable lazy language is Haskell
(and its web avatar PureScript). Although rare in general purpose languages,
lazy evaluation is more widespread in the configuration space: the configuration
languages Dhall, CUE and Jsonnet also implements full lazy evaluation. So are
the Nix language, which inspired Nickel, and Nickel itself.

@@

\subsection*{Unions}
Unions ($\cup$) are a fundamental building block of programs.
A union holds a value whose
shape is known to be in a fixed set of alterniteves, without exposing
which of those alternatives the value belongs to.
For example, a value that could be either a Number or a String can be
modelled using unions as \nickel{Num @| String}.
They correspond logically to disjunctions.

@@

They can also be used to combine records \unsure{Better
naming}. For instance, in Figure \ref{fig:intersection-record}
two types are defined \nickel{Animal} and \nickel{Pet}, and
a variable that is compatible with both types is declared, with
type \nickel{Animal @& Pet}.

>>>>

\subsection*{Purity}
\label{sec:optimizations}
\info{Present inlining and CSE as two major code
optimizations.
Purity and immutability as two important factors.}

\unsure{I (Arnaud) changed the title of this subsection. Maybe it's
  not the best one, but if it is, then we ought to reorder the section
  a little bit to fit the modified narrative.}

@@

Beyond CSE, optimizations such as loop-invariant code motion or
let-floating~\cite{letFloating} apply the same principle of extracting out an invariant
expression to avoid its recomputation respectively across loop iterations and
function calls.

@@

@@

\subsection*{Unions}
Unions ($\cup$) are a fundamental building block of programs.
A union holds a value whose
shape is known to be in a fixed set of alternatives, without exposing
which of those alternatives the value belongs to.
For example, a value that could be either a Number or a String can be
modelled using unions as \nickel{Num @| String}.
They correspond logically to disjunctions.

@@

They can also be used to combine dictionaries in an object-oriented fashion. For instance, in Figure \ref{fig:intersection-record}
two types are defined \nickel{Animal} and \nickel{Pet}, and
a variable that is compatible with both types is declared, with
type \nickel{Animal @& Pet}.
